Computer-Assisted Analysis of Emendations of G\"odel's Ontological Proof

### 2014-10-23 Papers/InProgress/LogicAndReligionCongress/Abstract.tex
Correct reference to Cocchiarella's semantics

The redundancy of A4 and A5 is particularly controversial. Magari \cite{TODO} claimed that the redundancy occurs already with Gödel's original axioms and definitions. Hájek \cite{Hajek 1996 TODO} investigated this further and claimed that Magari's claim is invalid, but true under the assumption of an additional axiom (PEP). Moreover, Hájek \cite{Hajek 1996 TODO} claimed that the redundancy occurs for Anderson's emended axioms and definitions \cite{Anderson 1990}. Anderson and Gettings \cite{AG1996, footnote 1, page 1} rebutted Hájek's claim, arguing that it holds only under constant domain semantics, while the emended argument by Anderson ought to be taken under Cocchiarella's semantics \cite{Cocchiarella} (a particular kind of varying domain semantics). Hájek \cite{Hajek 2002, page 7} acknowledges this rebuttal, and apparently accepts it, as evidenced by his use of A4 and A5 in his new small emendation (replacing A:A1 and A2 by a new axiom H:A12) of Anderson's variant with varying domains \cite{Hajek 2002, section 4}. Nevertheless, he does show yet another emended version where A4 and A5 are redundant, but A3 is replaced by a stronger axiom additionally stating that the property of actual existence is positive \cite{Hajek 2002, section 5}. Our results show that Hájek was originally right, under both constant and varying domain semantics with no need to strengthen A3 (though this need might exist when H:A12 is used instead of A:A1 and A2). It should be noted, however, that \cite{Anderson, footnote 14} vaguely remarks that only the quantifiers in T3' and in A:D2  need to be interpreted as actualistic quantifiers, while other may be taken as possibilistic quantifiers. We have inv  mixed variant.

>>>>

The redundancy of A4 and A5 is particularly controversial. Magari \cite{TODO} claimed that the redundancy occurs already with Gödel's original axioms and definitions. Hájek \cite{Hajek 1996 TODO} investigated this further and claimed that Magari's claim is invalid, but true under the assumption of an additional axiom (PEP). Moreover, Hájek \cite{Hajek 1996 TODO} claimed that the redundancy occurs for Anderson's emended axioms and definitions \cite{Anderson 1990}. Anderson and Gettings \cite{AG1996, footnote 1, page 1} rebutted Hájek's claim, arguing that it holds only under constant domain semantics, while the emended argument by Anderson ought to be taken under Cocchiarella's semantics \cite{Cocchiarella} (a varying domain semantics). Hájek \cite{Hajek 2002, page 7} acknowledges this rebuttal, and apparently accepts it, as evidenced by his use of A4 and A5 in his new small emendation (replacing A:A1 and A2 by a new axiom H:A12) of Anderson's variant with varying domains \cite{Hajek 2002, section 4}. Nevertheless, he does show yet another emended version where A4 and A5 are redundant, if A3 is replaced by a stronger axiom additionally stating that the property of actual existence is positive \cite{Hajek 2002, section 5}. Our results show that Hájek was originally right, under both constant and varying domain semantics with no need to strengthen A3 (though this need might exist when H:A12 is used instead of A:A1 and A2). It should be noted, however, that \cite{Anderson, footnote 14} vaguely remarks that only the quantifiers in T3' and in A:D2  need to be interpreted as actualistic quantifiers, while other may be taken as possibilistic quantifiers. We have inv  mixed variant.
